\Large\textbf{Advection versus diffusion in brain ventricular transport}

### 2025-04-07 paper/main.tex
Updates in Discussion 1

\subsection{The roles of advection and diffusion in brain ventricular solute transport}
To investigate brain ventricular solute transport, we quantified transport
based on changes in fluorescence intensity $\Delta F$ (experiments) and
mean concentration $\cbar$ (simulations) over time. Our results convincingly show that
the solute transport depends on a balance of advection and diffusion.
While advection is the strongest transport mechanism on a global scale for
the three solutes we studied (global Péclet numbers greater than unity),
diffusion is balancing out advection for shorter distances and in regions without motile cilia activity.
For instance, for the larger extracellular vesicles, no solute reached the (distant)
posterior ventricle (a distance of $L = 200$ \textmu m) within the simulation time (around 860 s).
Advective transport by the mean velocity $\overline{U}=2.4$ \textmu m/s over the same
distance would happen on a timescale of $t_a=L/\overline{U}=83$ s, indicating that
transport to the posterior ventricle is solely driven by diffusion at this developmental
stage. The estimated timescale of diffusion $t_d=L^2/D_1$ over the 
same distance is $\approx$24500 s, compared to 696 s and 348 s for the 
smaller proteins (STM-GFP and Dendra2).
This explains why $D_1$ is the only
case where no solute spreads to the posterior ventricle,
while STM-GFP and Dendra2 are transported there by diffusion.
Larger molecules transported primarily by advection
are thus more easily
compartmentalized within the ventricles
as a result of the compartmentalized CSF flow.

>>>>

\subsection{The roles of advection and diffusion in brain ventricular solute transport}

We quantified brain ventricular solute transport based on changes in
fluorescence intensity $\Delta F$ (experiments) and mean concentration
$\cbar$ (simulations) over time. Our results show that the solute
distribution depends on a balance between advection and diffusion.
While advection is the strongest transport mechanism on a global scale
for the three solutes we studied (global Péclet numbers $> 1$),
diffusion is balancing out advection for shorter distances and in
regions without motile cilia activity.  For instance, for the larger
extracellular vesicles, no solute reached the distant posterior
ventricle (a distance of $L = 200$ \textmu m) within the simulation
time (around 860 s). Advective transport by the mean velocity
$\overline{U}=2.4$ \textmu m/s over the same distance would occur on a
timescale of $t_a=L/\overline{U}=83$ s, indicating that transport to
the posterior ventricle is not driven by advection at this
developmental stage. The estimated timescale of diffusion for the
extracellular vesicles ($t_d=L^2/D_1$) over the same distance is 24500
s, but as low as 696 s and 348 s for the smaller proteins STM-GFP and
Dendra2, respectively. These estimates support our observations that
STM-GFP and Dendra2 spread to the posterior ventricle (by diffusion)
while the extracellular vesicles do not. Larger molecules transported
primarily by advection are thus more easily compartmentalized within
the ventricles as a result of the compartmentalized CSF flow.
